### 2021-03-19 notes/notes.tex
Added simulations, including some parallel stuff to run.
Also, embarassingly, I had forgotten to add the task file to the
git, even though it's been around for a while.

\section{Simulation results}

>>>>

\section{Simulation results}
\subsection{Effects of observation noise on inference}
Observation noise refers to the noise on the position of the hand. The generating process is a Gaussian with $\sigma = 0.1$, which is determined in ./code/adaptation/pars.py. However, the agent has a belief on this value, which is fixed for the agent. This value (obs_sd, which can be passed on instanciation) can be used in lieu of an explicit $\Delta t$ parameter which controls the size of the time step
